\section{Scheme Description}

First, some notation is defined for the scheme that follows:
\[
   \R^n \equiv \{\Psi^\pm\iL,\Psi^\pm\iR\} \quad\forall i
\]
\[
   \H^n \equiv \{\rho_i^n, (\rho u)_i^n, E_i^n\} \quad\forall i
\]
\[
   \delta e^n \equiv \{\delta e_i^n\} \quad\forall i
\]
\[
   \Delta^n \equiv \{\Delta\rho_i^n, \Delta(\rho u)_i^n, \Delta E_i^n\} \quad\forall i
\]
\[
   \sigma^n \equiv \{\sigma_{s,i,L}^n, \sigma_{s,i,R}^n,
   \sigma_{a,i,L}^n, \sigma_{a,i,R}^n, \sigma_{t,i,L}^n, \sigma_{t,i,R}^n\}
   \quad\forall i
\]
These are the quantities that are stored throughout the
calculation. Other quantities are computed when needed.

\begin{enumerate}

\item \textbf{Compute initial conditions.} The following initial conditions
are provided: $\R^0$, $\H^0$, $\sigma^0$, and $\delta e^0$.

\item \textbf{Begin transient.} For each time step $n$, a new time step
size must be computed in accordance with the CFL condition.

% Cycle 1 predictor

\item \textbf{Perform Cycle 1 Predictor.} This step goes from
$t^n$ to $t^{n+\fourth}$.

\begin{enumerate}
\item \textbf{Perform Cycle 1 MUSCL-Hancock Predictor.} First, slopes $\Delta^n$ are
computed.
Then a linear representation of the solution is created, and the
the MUSCL-Hancock predictor is performed to obtain $\H^*$, the
homogeneous hydrodyamics solution at $t^{n+\fourth}$.

\item \textbf{Initialize nonlinear iteration.} Iteration of the
$t^{n+\fourth}$ solution is required since the system of equations
is nonlinear. The iterates $\R^k$ and $\H^k$ may be initialized
to the previous time
values, $\R^n$ and $\H^n$, respectively.

\item\label{item:vel_update}
\textbf{Update velocities.} The Crank-Nicolson discretization
of the velocity update equation, Equation \requ{hydromCNfull},
is solved to obtain new
velocities at cell centers, $\{u_i^{k+1}\}$. Evaluation of
the cross sections and radiation quantities $\E$ and $\F$
is achieved by averaging the left and right values.

\item \textbf{Update radiation.} The Crank-Nicolson discretization of the S-2
equations, Equations \requ{S2CNfullL} and \requ{S2CNfullR} are solved, using
the linearization given in Section \ref{sec:linearization}. Evaluation
of the densities and velocities is achieved using using the cell-centered values
in conjunction with the slopes $\Delta^n$. Evaluation of internal
energies and temperatures is achieved using the internal energy slopes
$\delta e^n$.

\item \textbf{Update internal energies.} The internal energies are
updated in accordance with the linearization procedure given is Section
\ref{sec:linearization}. The update equations produce edge values
$\{e^{k+1}\iL,e^{k+1}\iR\}$. These left and right values are
averaged to produce cell average values for internal energy $\{e^{k+1}_i\}$
which are used in the subsequent iteration.
This is also the time when cross sections should be updated
if they are functions of the hydrodynamic state of the fluid.

\item \textbf{Check convergence.} The new solutions $\R^{k+1}$ and
$\H^{k+1}$ are compared with the previous iteration solutions
$\R^k$ and $\H^k$ to determine if convergence has been achieved.
If the solutions have not converged, then the computation
returns to Step \ref{item:vel_update}.
\end{enumerate}

% Cycle 1 corrector

\item \textbf{Perform Cycle 1 Corrector.} This step proceeds
just as the predictor step, except that the MUSCL-Hancock
corrector step is used instead of the MUSCL-Hancock predictor
step, and the step goes from $t^n$ to $t^{n+\half}$ instead
of $t^n$ to $t^{n+\fourth}$. No new slopes are computed;
evaluation of edge densities and velocities again use
$\Delta^n$, and evaluation of edge internal energies
and temperatures again use $\delta e^n$.

% Cycle 2 predictor

\item \textbf{Perform Cycle 2 Predictor.} This step proceeds
just as the Cycle 1 predictor step, except that the
step goes from $t^{n+\half}$ to $t^{n+\frac{3}{4}}$ instead
of $t^n$ to $t^{n+\fourth}$. As in Cycle 1, new slopes
are computed in the MUSCL-Hancock predictor step;
the slopes $\Delta^{n+\half}$ are then used for
evaluation of edge densities and velocities in the remainder
of the cycle. Evaluation of edge internal energies
and temperatures again use $\delta e^n$.

% Cycle 2 corrector

\item \textbf{Perform Cycle 2 Corrector.} This step goes
from $t^{n+\half}$ to $t^{n+1}$, but uses a form of
TR/BDF-2 instead of Crank-Nicolson, so values at $t^n$
are used in the temporal discretization.

% End

\item \textbf{Store values for next time step.}
At this point, the old solutions, hydrodynamics slopes,
internal energy slopes, and cross sections
are saved for the next time step.

\end{enumerate}
